An upper bound to gas storage and delivery via pressure-swing adsorption in porous materials

### 2021-03-12 gas-adsorption/referee-response.md

# Referee 3

Referee 3 states that the conclusions are convincing, and makes two suggestions
for improving the paper:

1. The referee suggests that we attempt to quantify the possible effect of a
   flexible MOF on our upper bound.

We have added a section "Flexible two-phase model" discussing flexible MOFs. We
cannot place a formal upper bound on a flexible MOF in general, but we can put
an upper bound on the capacity of a two-phase MOF such as Co(bdp), if we
constrain the free energy difference between the two phases. This suggests that
this type of a system will require a more stable closed phase in order to reach
the DOE targets.

1. The referee asks that we provide some guidelines in terms of working
   conditions to reach the DOE target.  They further suggest looking at a
   temperature difference to see how that could impact the deliverable capacity.

### 2021-03-12 gas-adsorption/rsc-gas-ads-complete.tex
add referee response about the flexible model

@@

\section{Flexible two-state model}

\begin{align}
    V_{\text{open}}|n(p_{hi})\V| &> |\Delta F| \\
    V_{\text{open}}|n(p_{lo})\V| &< |\Delta F|
\end{align}
This means that for a given $\Delta F$ we can put an upper bound on the
deliverable capacity.

\davidsays{This means we should pick the $\V$ to be big enough to make us just
on the boundary of not collapsing.  This means that:}
\begin{align}
    n(\mu_{lo} + \V)\V = \Delta F
\end{align}
This is a nonlinear equation that we want to solve.

\begin{figure}
    \centering
    \includegraphics[width=0.95\columnwidth]{methane-298-flexible}
    \caption{Deliverable capacity of methane in a flexible substrate at 298\ K as a function of the free energy difference 
      between open and closed phases. The experimental deliverable capacity for Co(bdp) is shown for
       comparison~\cite{fixme}, along with the free energy difference between open and closed conformations~\cite{fixthis}.}
    \label{fig:methane-flexible}
\end{figure}

@@

>>>>

\usepackage[color]{changebar}
\cbcolor{red}

@@

\cbstart
\section{Flexible two-phase model}
\begin{figure}
    \centering
    \includegraphics[width=0.95\columnwidth]{methane-298-flexible}
    \caption{Deliverable capacity of methane in a flexible substrate at 298\ K as a function of the free energy difference 
      between open and closed phases. The experimental deliverable capacity for Co(bdp) is shown for
       comparison~\cite{fixme}, along with the free energy difference between open and closed conformations~\cite{fixthis}.}
    \label{fig:methane-flexible}
\end{figure}
Although our limit does not directly apply to materials that change conformation in
response to gas adsorption, we can make an estimate of the benefits to be gained
materials such as \davidsays{FIXME AND CITE} which undergo a phase change in the
presence of gas.  We can model such a material as a two-phase system with one ``open''
phase and a ``closed'' phase in which all gas is expelled.  We assume there is a
free energy difference $\Delta G$ between the two phases in the absence of gas, with
the closed phase more stable.  In addition, we assume a $\V$ as above \davidsays{REFERENCE EQUATION?}
for the adsorption of gas into the open phase.  In order for the system to benefit
from the two phases, the open phase must be preferred at $\pfull$, with the closed phase
preferred at $\pempty$.  This requires that
\begin{align}
    V_{\text{open}}|\rho_{\text{open}}(\pfull)\V| &> |\Delta G| \\
    V_{\text{open}}|\rho_{\text{open}}(\pempty)\V| &< |\Delta G|
\end{align}
where $\rho_{\text{open}}(p)$ is the density of gas in the open phase of the material at
the given pressure.  This model has no upper bound on the deliverable capacity, since
$\V$ and $\Delta G$ can together be increased without bound.  We can, however, place a
bound for a fixed $\Delta G$, since if the gas is too strongly attracted to the open phase
the material will remain open at $\pempty$.  This upper bound is found by identifying the
attractive interaction $\V$ that solves the equation
\begin{align}
    \rho(\muempty{} + \V)\V = \Delta G/V_{\text{open}}
\end{align}
for $\V$, which gives the largest attraction consistent with the material closing
at the empty pressure.
Figure~\ref{fig:methane-flexible} illustrates
how this upper bound depends on $\Delta G$ for methane.  For comparison, we include the free energy
difference for Co(bdp)~\davidsays{CITE} and its measured deliverable capacity.  While this
upper bound is not rigorous, it suggests that a two-phase flexible material for methane storage
would benefit from significantly greater stability of the closed phase---provided the open phase
had correspondingly greater attraction for the gas molecules.  Figure~\ref{fig:hydrogen-flexible}
shows the corresponding result for hydrogen storage, indicating that for a flexible material to
reach the DOE ULTIMATE deliverable capacity would require far greater stability for the closed
phase, as well as an unprecedented level of attractive interaction for hydrogen.

@@

\cbend
